---
title: "Process data from reaction times to D scores and PI scores"
author: "Ian Hussey"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

Scored data isn't used directly in our analyses, but is likely to have high reuse potential as D and PI scored data is what is typically analyzed.

```{r, include=FALSE}
knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)
```

```{r}

# set seed for computational reproducibility
set.seed(42)

# dependencies
library(tidyverse)
library(knitr)
library(kableExtra)
library(janitor)

# function to round all numeric vars in a data frame
round_df <- function(df, n_digits = 3) {
  df %>% mutate_if(is.numeric, janitor::round_half_up, digits = n_digits)
}

# using Ruscio's own code
# implementation of the PI, which goes by many names, including "ruscio's A".
ruscios_A_function <- function(x, y) {
    nx <- length(x)
    ny <- length(y)
    rx <- sum(rank(c(x, y))[1:nx])
    A = (rx / nx - (nx + 1) / 2) / ny
    return(A)
}

ruscios_A <- function(data, variable = "rt", group = "block_type", value1 = "inconsistent", value2 = "consistent") {
  # Ensure data is a data frame (e.g., not a tbl_data)
  data <- as.data.frame(data)
  # Select the observations for group 1
  x <- data[data[[group]] == value1, variable]
  # Select the observations for group 2
  y <- data[data[[group]] == value2, variable]
  A.obs <- ruscios_A_function(x, y)
  return(as.numeric(A.obs))
}

# table format in output
options(knitr.table.format = "html") 

```

# Get trial level data

```{r}

data_all <- read.csv("../trial level/data_trial_level.csv") 

```

# Calculate scores

Not employed for the test-retest analyses but may be useful for others to reuse.

## D scores

See Hussey, Thompson et al (2017) Interpreting and inverting with less cursing: A guide to interpreting IRAP data

```{r}

data_D_scores_overall <- data_all %>%
  filter(rt <= 10000) %>%
  group_by(unique_id, timepoint) %>%
  summarize(mean_con = mean(rt[block_type == "consistent"], na.rm = TRUE),
            mean_incon = mean(rt[block_type == "inconsistent"], na.rm = TRUE),
            sd = sd(rt, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(D = (mean_incon - mean_con)/sd) %>%
  select(unique_id, timepoint, D_overall = D) 

data_D_scores_trial_type <- data_all %>%
  filter(rt <= 10000) %>%
  group_by(unique_id, timepoint, trial_type) %>%
  summarize(mean_con = mean(rt[block_type == "consistent"], na.rm = TRUE),
            mean_incon = mean(rt[block_type == "inconsistent"], na.rm = TRUE),
            sd = sd(rt, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(D = (mean_incon - mean_con)/sd) %>%
  select(unique_id, timepoint, trial_type, D) %>%
  spread(trial_type, D) %>%
  rename(D_tt1 = tt1,
         D_tt2 = tt2,
         D_tt3 = tt3,
         D_tt4 = tt4) 

```

## PI scores

See De Schryver et al., (2017) The PIIRAP: An alternative scoring algorithm for the IRAP using a probabilistic semiparametric effect size measure

```{r}

data_PI_scores_overall <- data_all %>%
  group_by(unique_id, timepoint) %>%
  do(PI_overall = ruscios_A(data = .)) %>%
  ungroup() %>%
  mutate(PI_overall = as.numeric(PI_overall)) 

data_PI_scores_trial_type <- data_all %>%
  group_by(unique_id, timepoint, trial_type) %>%
  do(PI = ruscios_A(data = .)) %>%
  ungroup() %>%
  mutate(PI = as.numeric(PI)) %>%
  spread(trial_type, PI) %>%
  rename(PI_tt1 = tt1,
         PI_tt2 = tt2,
         PI_tt3 = tt3,
         PI_tt4 = tt4) 

```

## Combine

```{r}

data_scored <- data_D_scores_overall %>%
  full_join(data_D_scores_trial_type, by = c("unique_id", "timepoint")) %>%
  full_join(data_PI_scores_overall, by = c("unique_id", "timepoint")) %>%
  full_join(data_PI_scores_trial_type, by = c("unique_id", "timepoint")) %>%
  left_join(data_all |>
              select(unique_id, 
                     domain, 
                     age, 
                     gender, 
                     block_order, 
                     trials_per_block, 
                     #number_of_pairs_of_test_blocks, 
                     #response_option_locations,
                     met_performance_criteria_typical,
                     met_performance_criteria_stricter) |>
              distinct(unique_id, .keep_all = TRUE), 
            by = "unique_id") %>%
  select(unique_id, timepoint, 
         domain, 
         age, gender, 
         block_order, 
         met_performance_criteria_typical,
         met_performance_criteria_stricter,
         D_overall, D_tt1, D_tt2, D_tt3, D_tt4,
         PI_overall, PI_tt1, PI_tt2, PI_tt3, PI_tt4)

write_csv(data_scored, "data_scored.csv")

# data_scored <- read_csv("data_scored.csv")

```

# Session info

```{r}

sessionInfo()

```


