---
title: "Recreation of Greenwald & Lai's (2020) meta-analyses of the IRAP's reliability using their data"
author: "Ian Hussey"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r, include=FALSE}
knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)
```

```{r}

# dependencies
library(tidyverse)
library(metafor)
library(knitr)
library(kableExtra)
library(psych)
library(janitor)

# function to round all numeric vars in a data frame
round_df <- function(df, n_digits = 3) {
  df %>% mutate_if(is.numeric, janitor::round_half_up, digits = n_digits)
}

apa_p_value <- function(p){
  p_formatted <- ifelse(p >= 0.001, paste("=", janitor::round_half_up(p, 3)),
                        ifelse(p < 0.001, "< .001", NA))
  p_formatted <- gsub(pattern = "0.", replacement = ".", x = p_formatted, fixed = TRUE)
  p_formatted
}

probability_of_superiority_function <- function(x, y) {
  nx <- length(x)
  ny <- length(y)
  rx <- sum(rank(c(x, y))[1:nx])
  A = (rx / nx - (nx + 1) / 2) / ny
  return(A)
}

spearman_brown_correction <- function(r_pearson) {
  inversion <- ifelse(r_pearson < 0, -1, 1)
  val <- janitor::round_half_up(2*abs(r_pearson)/(1 + abs(r_pearson)), 2)
  return(val*inversion)
}

add_heterogeneity_metrics_to_forest <- function(fit) {
  ## more detailed
  # bquote(paste("RE Model (Q(df = ", .(formatC(fit$k - 1)), ") = ", 
  #              .(formatC(janitor::round_half_up(fit$QE, 2))), 
  #              ", p ", .(formatC(apa_p_value(fit$QEp))),
  #              ", ", tau^2, " = ", .(formatC(janitor::round_half_up(fit$tau2, 1))), 
  #              ", ", I^2, " = ", .(formatC(janitor::round_half_up(fit$I2, 1))),
  #              "%, ", H^2," = ", .(formatC(janitor::round_half_up(fit$H2, 1))), ")"))
  ## less detailed
  bquote(paste("RE Model (", tau^2, " = ", .(formatC(janitor::round_half_up(fit$tau2, 1))), 
               ", ", I^2, " = ", .(formatC(janitor::round_half_up(fit$I2, 1))),
               "%, ", H^2," = ", .(formatC(janitor::round_half_up(fit$H2, 1))), ")"))
}

# table format in output
options(knitr.table.format = "html") 

```

# Internal consistency

## Get data & do exclusions

Two different data sources (datasets that were had their initial cleaning and organizing done at different times): do final cleaning on these and add them together.

```{r}

data_lai_ic <- read.csv("../data/lai_meta_irap_ic.csv") 

```

## Demographics & Ns

```{r}

data_lai_ic %>%
  summarize(n = sum(ni)) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

```

## Meta analysis

Variance associated with each effect size calculated mathematically using the Fischer's r-to-z esimate (i.e., pearson's r converted to spearman brown r converted to fischer's r-to-z) and N.

```{r fig.height=8, fig.width=8}

# calculate internal consistencies
fit_lai_ic <- data_lai_ic %>%
  escalc(measure = "ZCOR", 
         ri = yi,
         ni = ni,
         data = ., 
         digits = 8) %>%
  rma(yi   = yi, 
      vi   = vi, 
      data = .,
      slab = article)

# make predictions 
predictions_ic <-
  predict(fit_lai_ic, digits = 5) %>%
  as.data.frame() %>%
  round_df(2)

# plot
metafor::forest(fit_lai_ic,
                xlab = "Internal Consistency [metric?]",
                addcred = TRUE,
                refline = FALSE,
                transf = transf.ztor,
                xlim = c(-3.75, 2.5),
                at = c(-1, -0.5, 0, 0.5, 1),
                mlab = add_heterogeneity_metrics_to_forest(fit_lai_ic))
text(-3.75, 27, "Study", pos = 4)
text(2.5, 27, "??? [95% CI]", pos = 2)

# summarize results
meta_effect_ic <- 
  paste0("Meta analysis: k = ", fit_lai_ic$k, 
         ", alpha = ",  janitor::round_half_up(transf.ztor(predictions_ic$pred), 2), 
         ", 95% CI [", janitor::round_half_up(transf.ztor(predictions_ic$ci.lb), 2), ", ", 
         janitor::round_half_up(transf.ztor(predictions_ic$ci.ub), 2), "]", 
         ", 95% CR [", janitor::round_half_up(transf.ztor(predictions_ic$pi.lb), 2), ", ", 
         janitor::round_half_up(transf.ztor(predictions_ic$pi.ub), 2), "]") 

meta_heterogeneity_ic <- 
  paste0("Heterogeneity tests: Q(df = ", fit_lai_ic$k - 1, ") = ", janitor::round_half_up(fit_lai_ic$QE, 2), 
         ", p ", ifelse(fit_lai_ic$QEp < 0.0001, "< .0001", paste0("= ", as.character(janitor::round_half_up(fit_lai_ic$QEp, 4)))),
         ", tau^2 = ", janitor::round_half_up(fit_lai_ic$tau2, 2), 
         ", I^2 = ",   janitor::round_half_up(fit_lai_ic$I2, 2),
         "%, H^2 = ",   janitor::round_half_up(fit_lai_ic$H2, 2))

```

Meta effect: `r meta_effect_ic`.

Heterogeneity: `r meta_heterogeneity_ic`.


# Test-retest reliability

## Get data 

```{r}

data_lai_trt <- read.csv("../data/lai_meta_irap_trt.csv") 

```

## Demographics & Ns

```{r}

data_lai_trt %>%
  summarize(n = sum(ni)) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

```

## Meta-analysis

Variance associated with each effect size calculated mathematically using the effect size and sample size.

```{r fig.height=3.2, fig.width=8}

# fit random Effects model 
fit_lai_trt <- data_lai_trt %>%
  escalc(measure = "ZCOR", 
         ri = yi,
         ni = ni,
         data = ., 
         digits = 8) %>%
  rma(yi   = yi, 
      sei  = vi, 
      data = .,
      slab = article)

# make predictions 
predictions_trt <-
  predict(fit_lai_trt, digits = 5) %>%
  as.data.frame() %>%
  round_df(2) 

# plot
metafor::forest(fit_lai_trt,
                xlab = "Test-retest reliability [[metric?]]",
                addcred = TRUE,
                refline = FALSE,
                xlim = c(-1.5, 1.7),
                at = c(0.0, 0.2, 0.4, 0.6, 0.8, 1.0),
                mlab = add_heterogeneity_metrics_to_forest(fit_lai_trt))
text(-1.5, 7, "Study", pos = 4)
text(1.7, 7, "??? [95% CI]", pos = 2)

# summarize results
meta_effect_trt <- 
  paste0("Meta analysis: k = ", fit_lai_trt$k, 
         ", rho = ",  janitor::round_half_up(transf.ztor(predictions_trt$pred), 2), 
         ", 95% CI [", janitor::round_half_up(transf.ztor(predictions_trt$ci.lb), 2), ", ", 
         janitor::round_half_up(transf.ztor(predictions_trt$ci.ub), 2), "]", 
         ", 95% CR [", janitor::round_half_up(transf.ztor(predictions_trt$pi.lb), 2), ", ", 
         janitor::round_half_up(transf.ztor(predictions_trt$pi.ub), 2), "]") 

meta_heterogeneity_trt <- 
  paste0("Heterogeneity tests: Q(df = ", fit_lai_trt$k - 1, ") = ", janitor::round_half_up(fit_lai_trt$QE, 2), 
         ", p ", ifelse(fit_lai_trt$QEp < 0.0001, "< .0001", paste0("= ", as.character(janitor::round_half_up(fit_lai_trt$QEp, 4)))),
         ", tau^2 = ", janitor::round_half_up(fit_lai_trt$tau2, 2), 
         ", I^2 = ",   janitor::round_half_up(fit_lai_trt$I2, 2),
         "%, H^2 = ",   janitor::round_half_up(fit_lai_trt$H2, 2))

# write to disk for pdf plots
write_rds(fit_lai_trt, "models/fit_lai_trt.rds")

```

Meta effect: `r meta_effect_trt`.

Heterogeneity: `r meta_heterogeneity_trt`.


