---
title: "Meta analyses of the IRAP's reliability"
subtitle: "Scores for each individual trial type"
author: "Ian Hussey"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r, include=FALSE}
knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)
```

```{r}

set.seed(42)

# dependencies
library(tidyverse)
library(metafor)
library(knitr)
library(kableExtra)
library(psych)
library(ggExtra)
library(scales) 
library(janitor)
library(parallel)
#library(ggtext) # devtools::install_github("clauswilke/ggtext")


# function to round all numeric vars in a data frame
round_df <- function(df, n_digits = 3) {
  df %>% mutate_if(is.numeric, janitor::round_half_up, digits = n_digits)
}

probability_of_superiority_function <- function(x, y) {
  nx <- length(x)
  ny <- length(y)
  rx <- sum(rank(c(x, y))[1:nx])
  A = (rx / nx - (nx + 1) / 2) / ny
  return(A)
}

spearman_brown_correction <- function(r_pearson) {
  inversion <- ifelse(r_pearson < 0, -1, 1)
  val <- janitor::round_half_up(2*abs(r_pearson)/(1 + abs(r_pearson)), 2)
  return(val*inversion)
}

apa_p_value <- function(p){
  p_formatted <- ifelse(p >= 0.001, paste("=", janitor::round_half_up(p, 3)),
                        ifelse(p < 0.001, "< .001", NA))
  p_formatted <- gsub(pattern = "0.", replacement = ".", x = p_formatted, fixed = TRUE)
  p_formatted
}

add_heterogeneity_metrics_to_forest <- function(fit) {
  bquote(paste("RE Model (", tau^2, " = ", .(formatC(janitor::round_half_up(fit$tau2, 2))), 
               ", ", I^2, " = ", .(formatC(janitor::round_half_up(fit$I2, 1))),
               "%, ", H^2," = ", .(formatC(janitor::round_half_up(fit$H2, 2))), ")"))
}

# table format in output
options(knitr.table.format = "html") 

# create directory needed to save output
dir.create("models")
dir.create("plots")

```

# Data 

```{r}

data_D_scores_internal_consistency_permuted_estimates <-
  read_csv("../data/effect sizes for meta-analyses/data_D_scores_internal_consistency_permuted_estimates_trial_types.csv")

data_D_scores_test_retest_icc <- 
  read_csv("../data/effect sizes for meta-analyses/data_D_scores_test_retest_icc_trial_types.csv")

```

# Internal consistency

Three methods of calculating internal consistency for the Implicit Relational Assessment Procedure (IRAP): 
- Odd vs even trials (mostly commonly reported in literature)
- First vs second half of task (more common for the most popular implicit measure, the IAT; would allow a like-for-like comparison)
- Cronbach's alpha via permutation (most robust)

The IRAP effect is most often quantified using the D1 scoring algorithm (Greenwald, Banaji & Nosek, 2003). i.e., trim all RTs > 10,000 ms, then D1 = (mean RT in the inconsistent blocks - mean RT in the consistent blocks)/SD of RTs in both block types. D1 scores are used throughout. Because of this, it wasn't possible to use Sam Parson's splithalf R package. A workflow for permutation-based alpha estimation using D scores is provided below.  

In each case, correlations between D scores calculated from the split halves are calculated, and then the Spearman-Brown prophecy formula is applied, i.e., r_sb = 2*r_pearson / (1+r_pearson). Importantly, this correction is applied to the absolute value of the pearson's correlation, and then its sign is corrected to be congruent with the pearson's correlation. This ensures that r_sb has a possible range of -1 to +1, as correlations should (whereas correction of native negative correlations allow for a lower limit of -Inf). I haven't seen this treatment of SB corrections applied to negative correlations well explicated elsewhere, so it is important to note here. 

For meta analysis, spearman brown correlations are converted to Fischers r-to-z for meta analysis. Estimates of the meta effect are then converted back for reporting. Heterogeneity metrics represent heterogeneity in Fischer's r-to-z estimates. See [here](https://stats.stackexchange.com/questions/26485/does-transformation-of-r-into-fisher-z-benefit-a-meta-analysis).

## Permutation-based split half correlations

ie an estimate of alpha through large number number of random half splits (see Parsons, Kruijt, & Fox. 2019). Estimate of alpha obtained via mean of the resampled Spearman-Brown corrected split half correlations, when calculating D1 scores for each half and sampling 10000 permutations.  

### Bonett transformations, all domains

```{r fig.height=6, fig.width=8}

data_ic_permuted <- data_D_scores_internal_consistency_permuted_estimates %>%
  mutate(se = (alpha_ci_upper - alpha_ci_lower)/(1.96*2))

# fit random Effects model 
fit_internal_consistency_permuted_estimates <- 
  rma.mv(yi     = yi, 
         V      = vi, 
         random = ~ 1 | domain,
         data   = data_ic_permuted,
         slab   = domain)

# make predictions 
predictions_permutations <-
  predict(fit_internal_consistency_permuted_estimates, digits = 5) %>%
  as.data.frame() %>%
  round_df(2)

# plot
metafor::forest(data_ic_permuted$yi, 
                data_ic_permuted$vi,
                xlim = c(-0.5, 1.5), # adjust horizontal plot region limits
                transf = transf.iabt,
                xlab = bquote(paste("Cronbach's ", alpha)),
                #at = c(0, 0.2, 0.4, 0.6, 0.8, 1),
                at = c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1.0),
                order = "obs", # order by size of yi
                slab = NA, 
                annotate = FALSE, # remove study labels and annotations
                efac = 0, # remove vertical bars at end of CIs
                pch = 19, # changing point symbol to filled circle
                col = "gray40", # change color of points/CIs
                psize = 2, # increase point size
                cex.lab = 1, cex.axis = 1, # increase size of x-axis title/labels
                lty = c("solid", "blank")) # remove horizontal line at top of plot
points(sort(transf.iabt(data_ic_permuted$yi)), 
       nrow(data_ic_permuted):1, pch = 19, cex = 0.5) # draw points one more time to make them easier to see
addpoly(fit_internal_consistency_permuted_estimates, mlab = "", cex = 1, addcred = TRUE) # add summary polygon at bottom and text
#text(0, -1, "RE Model", pos = 4, offset = 0, cex = 1)

# summarize results
meta_effect_ic <- 
  paste0("Meta analysis: k = ", fit_internal_consistency_permuted_estimates$k, 
         ", alpha = ",  janitor::round_half_up(transf.iabt(predictions_permutations$pred), 2), 
         ", 95% CI [", janitor::round_half_up(transf.iabt(predictions_permutations$ci.lb), 2), ", ", 
         janitor::round_half_up(transf.iabt(predictions_permutations$ci.ub), 2), "]", 
         ", 95% CR [", janitor::round_half_up(transf.iabt(predictions_permutations$pi.lb), 2), ", ", 
         janitor::round_half_up(transf.iabt(predictions_permutations$pi.ub), 2), "]") 

# save to disk for making pdf plot
#write_rds(fit_internal_consistency_permuted_estimates, "models/fit_internal_consistency_permuted_estimates.rds")

```

```{r eval=FALSE, fig.height=18, fig.width=7, include=FALSE}

metafor::forest(data_ic_permuted$yi, 
                data_ic_permuted$vi,
                slab = paste(data_ic_permuted$domain, data_ic_permuted$trial_type), 
                transf = transf.iabt,
                order = "obs")

```

Meta effect: `r meta_effect_ic`.

### Sensitivity analyses

#### Bonett transformations, excluding sexuality domain (as in main analaysis's sensitivity analysis)

```{r fig.height=6, fig.width=8}

data_ic_permuted_sensitivity <- data_D_scores_internal_consistency_permuted_estimates %>%
  filter(!str_detect(domain, "Sexuality")) |>
  mutate(se = (alpha_ci_upper - alpha_ci_lower)/(1.96*2))

# fit random Effects model 
fit_internal_consistency_permuted_estimates_sensitivity <- 
  rma.mv(yi     = yi, 
         V      = vi, 
         random = ~ 1 | domain,
         data   = data_ic_permuted_sensitivity,
         slab   = domain)

# make predictions 
predictions_permutations_sensitivity <-
  predict(fit_internal_consistency_permuted_estimates_sensitivity, digits = 5) %>%
  as.data.frame() %>%
  round_df(2)

# plot
metafor::forest(data_ic_permuted_sensitivity$yi, 
                data_ic_permuted_sensitivity$vi,
                xlim = c(-0.5, 1.5), # adjust horizontal plot region limits
                transf = transf.iabt,
                xlab = bquote(paste("Cronbach's ", alpha)),
                #at = c(0, 0.2, 0.4, 0.6, 0.8, 1),
                at = c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1.0),
                order = "obs", # order by size of yi
                slab = NA, 
                annotate = FALSE, # remove study labels and annotations
                efac = 0, # remove vertical bars at end of CIs
                pch = 19, # changing point symbol to filled circle
                col = "gray40", # change color of points/CIs
                psize = 2, # increase point size
                cex.lab = 1, cex.axis = 1, # increase size of x-axis title/labels
                lty = c("solid", "blank")) # remove horizontal line at top of plot
points(sort(transf.iabt(data_ic_permuted_sensitivity$yi)), 
       nrow(data_ic_permuted_sensitivity):1, pch = 19, cex = 0.5) # draw points one more time to make them easier to see
addpoly(fit_internal_consistency_permuted_estimates_sensitivity, mlab = "", cex = 1, addcred = TRUE) # add summary polygon at bottom and text
#text(0, -1, "RE Model", pos = 4, offset = 0, cex = 1)

# summarize results
meta_effect_sensitivity <- 
  paste0("Meta analysis: k = ", fit_internal_consistency_permuted_estimates_sensitivity$k, 
         ", alpha = ",  janitor::round_half_up(transf.iabt(predictions_permutations_sensitivity$pred), 2), 
         ", 95% CI [", janitor::round_half_up(transf.iabt(predictions_permutations_sensitivity$ci.lb), 2), ", ", 
         janitor::round_half_up(transf.iabt(predictions_permutations_sensitivity$ci.ub), 2), "]", 
         ", 95% CR [", janitor::round_half_up(transf.iabt(predictions_permutations_sensitivity$pi.lb), 2), ", ", 
         janitor::round_half_up(transf.iabt(predictions_permutations_sensitivity$pi.ub), 2), "]") 

# save to disk for making pdf plot
#write_rds(fit_internal_consistency_permuted_estimates_sensitivity, "models/fit_internal_consistency_permuted_estimates_sensitivity.rds")

```

```{r eval=FALSE, fig.height=18, fig.width=7, include=FALSE}

metafor::forest(data_ic_permuted_sensitivity$yi, 
                data_ic_permuted_sensitivity$vi,
                slab = paste(data_ic_permuted_sensitivity$domain, data_ic_permuted_sensitivity$trial_type), 
                transf = transf.iabt,
                order = "obs")

```

Meta effect: `r meta_effect_sensitivity`.

# Test-retest reliability

## Intraclass Correlations

"It has been argued that test-retest reliability should reflect absolute agreement, rather than consistency, between measurements (Koo & Li, 2016). For example, a perfect correlation between scores at two time points may occur also when there is a systematic difference between time points (i.e. a difference that is about equal for all participants)." (Parsons, Kruijt, & Fox, 2019).
Absolute agreement therefore also takes within-participant changes into account in its denominator, where consistency does not.

```{r fig.height=8.5, fig.width=8}

# fit random Effects model 
fit_test_retest_icc <- 
  rma.mv(yi     = ICC, 
         V      = se^2, 
         random = ~ 1 | domain,
         data   = data_D_scores_test_retest_icc,
         slab   = domain)

# make predictions 
predictions_test_retest_icc <-
  predict(fit_test_retest_icc, digits = 5) %>%
  as.data.frame() %>%
  round_df(2) 

# plot
metafor::forest(fit_test_retest_icc,
                xlab = "Intraclass Correlation",
                addcred = TRUE,
                refline = FALSE,
                xlim = c(-3, 2.3),
                #at = c(-1, -0.75, -0.5, -0.25, 0, 0.25, 0.5, 0.75, 1),
                at = c(-1, -0.5, 0, 0.5, 1))
                #mlab = add_heterogeneity_metrics_to_forest(fit_test_retest_icc))
text(-3, 34, "Study", pos = 4)
text(2.3, 34, "ICC2 [95% CI]", pos = 2)

# summarize results
meta_effect_trt <- 
  paste0("Meta analysis: k = ", fit_test_retest_icc$k, 
         ", ICC2 = ",  janitor::round_half_up(predictions_test_retest_icc$pred, 2), 
         ", 95% CI [", janitor::round_half_up(predictions_test_retest_icc$ci.lb, 2), ", ", 
         janitor::round_half_up(predictions_test_retest_icc$ci.ub, 2), "]", 
         ", 95% CR [", janitor::round_half_up(predictions_test_retest_icc$pi.lb, 2), ", ", 
         janitor::round_half_up(predictions_test_retest_icc$pi.ub, 2), "]") 

# write to disk for pdf plots
#write_rds(fit_test_retest_icc, "models/fit_test_retest_icc.rds")

```

Meta effect: `r meta_effect_trt`.

# Session info

```{r}

sessionInfo()

```

