---
title: "Data tidying"
author: "Ian Hussey"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

This code is ugly, sorry. The data files for each study were manually processed reshaped in slightly different ways, meaning that slightly different code is needed to tidy each of them. Also, the code to tidy them was written across many years, as my skill improved. So, different methods are employed between datasets to effect the same results, and there is more repetition than there should be. I blame the format of the old IRAP data files for this headache.

```{r, include=FALSE}
knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)
```

```{r}

library(tidyverse)
library(readxl)
library(janitor)

```

# Task parameters

```{r}

# task parameters
data_task_parameters <- read_excel("../../measures/IRAP procedural parameters, stimuli, and publication status.xlsx") %>%
  clean_names() %>%
  select(domain, 
         trials_per_block, 
         response_option_locations, 
         block_order_between_participants = block_order,
         data_published,	
         measure_published) %>%
  mutate_all(funs(str_replace(., "NA", NA_character_))) |>
  mutate(data_published = !is.na(data_published),
         measure_published = !is.na(measure_published))

```

# IRAP 2012 VB6 format files

## Evaluative IRAPs

```{r}

wrangle_data <- function(file, n_stimulus_exemplars = 6, timepoint = 1){
  
  temp <- 
    read_csv(file, show_col_types = FALSE) |>
    mutate(participant = as.factor(participant)) |>
    select(-contains("fp_"), -block_order) |>
    mutate_at(vars(starts_with("t")), funs(str_replace(., "Correct", "1"))) |>
    mutate_at(vars(starts_with("t")), funs(str_replace(., "Wrong", "0"))) |>
    mutate_at(vars(starts_with("t")), funs(as.numeric)) |>
    mutate_at(vars(experiment, participant, data_type), as.character) |>
    filter(grepl("Target", data_type)) |>
    right_join(read_csv(file, show_col_types = FALSE) |>
                 mutate(participant = as.factor(participant)) |>
                 select(participant, block_order) |>
                 distinct(participant, .keep_all = TRUE), by = "participant") |>
    mutate(block_order = dplyr::recode(block_order,
                                       "The Consistent-First Sequence was Selected" = "consistent first",
                                       "The Inconsistent-First Sequence was Selected" = "inconsistent first",
                                       "Consistant" = "consistent first",
                                       "Inconsistant" = "inconsistent first")) |>
    mutate(experiment = str_remove(experiment, "[12]"),
           timepoint = timepoint) |>
    # wrangle acc vs rt
    mutate(data_type = str_replace(data_type, "Target ", "target"),
           data_type = str_replace(data_type, "Raw Latency", "rt"),
           data_type = str_remove(data_type, ":"),
         data_type = str_replace(data_type, "Accuracy", "accuracy")) |>
    separate(data_type, into = c("stimulus_number", "data_type"), sep = " ") |>
    # remove rows containing non data
    mutate(exclude = case_when(data_type == "accuracy" &
                                 is.na(t2_c_tt1) &
                                 is.na(t2_c_tt2) &
                                 is.na(t2_c_tt3) &
                                 is.na(t2_c_tt4) &
                                 is.na(t2_ic_tt1) &
                                 is.na(t2_ic_tt2) &
                                 is.na(t2_ic_tt3) &
                                 is.na(t2_ic_tt4) ~ TRUE,
                               data_type == "rt" &
                                 t2_c_tt1 == 0 &
                                 t2_c_tt2 == 0 &
                                 t2_c_tt3 == 0 &
                                 t2_c_tt4 == 0 &
                                 t2_ic_tt1 == 0 &
                                 t2_ic_tt2 == 0 &
                                 t2_ic_tt3 == 0 &
                                 t2_ic_tt4 == 0 ~TRUE,
                               TRUE ~ FALSE)) |>
    filter(exclude == FALSE) |>
    select(-exclude) |>
    # remove redundant rows
    filter(stimulus_number %in% paste0("target", seq(1:n_stimulus_exemplars)))
  
  
  result <- temp |>
    # keep only participants with the correct number of rows
    semi_join(temp |>
                count(participant, timepoint) |>
                filter(n == n_stimulus_exemplars*2),
              by = c("participant", "timepoint")) |>
    select(experiment, participant, timepoint, block_order,
           stimulus_number, data_type, 
           t1_c_tt1, t1_c_tt2, t1_c_tt3, t1_c_tt4, 
           t1_ic_tt1, t1_ic_tt2, t1_ic_tt3, t1_ic_tt4, 
           t2_c_tt1, t2_c_tt2, t2_c_tt3, t2_c_tt4, 
           t2_ic_tt1, t2_ic_tt2, t2_ic_tt3, t2_ic_tt4, 
           t3_c_tt1, t3_c_tt2, t3_c_tt3, t3_c_tt4, 
           t3_ic_tt1, t3_ic_tt2, t3_ic_tt3, t3_ic_tt4) |>
    pivot_longer(cols = starts_with("t1") | starts_with("t2") | starts_with("t3"),
                 names_to = "key",
                 values_to = "value") |>
    pivot_wider(names_from = data_type,
                values_from = value) |>
    separate(key, into = c("block_number", "block_type", "trial_type"), sep = "_") |>
    mutate(block_number = as.numeric(str_remove(block_number, "t")),
           block_type = dplyr::recode(block_type,
                                      "c" = "consistent",
                                      "ic" = "inconsistent")) |>
    # where participant code was missing it appears as 0. so, exclude zeros
    filter(participant != 0)
  
  return(result)
  
}

# temp <- read_csv("raw/IRAP 2012 VB6 format files/chad political attitudes 2016.csv") |>
#   select(-stimuli_category_1) |>
#   right_join(read_csv("raw/IRAP 2012 VB6 format files/chad political attitudes 2016.csv") %>%
#                mutate(participant = as.factor(participant)) %>%
#                select(participant, stimuli_category_1) %>%
#                drop_na() %>%
#                distinct(participant, .keep_all = TRUE), by = "participant") %>%
#   mutate(experiment = case_when(stimuli_category_1 == "Hillary Clinton" ~ "clinton_trump",
#                                 stimuli_category_1 == "man" ~ "men_women",
#                                 stimuli_category_1 == "rich people" ~ "rich_poor"))
# 
# write_csv(temp, "raw/IRAP 2012 VB6 format files/chad political attitudes 2016 fixed experiment.csv")

chad_political_attitudes <- wrangle_data(file = "raw/IRAP 2012 VB6 format files/chad political attitudes 2016.csv")

chad_mental_illness_stigma <- wrangle_data(file = "raw/IRAP 2012 VB6 format files/chad mental illness stigma.csv", 
                                           n_stimulus_exemplars = 8)

chad_bodyImage_IRAP1 <- wrangle_data(file = "raw/IRAP 2012 VB6 format files/chad body image t1.csv", 
                                     timepoint = 1)

chad_bodyImage_IRAP2 <- wrangle_data(file = "raw/IRAP 2012 VB6 format files/chad body image t2.csv", 
                                     timepoint = 2)

chad_gender_IRAP1 <- wrangle_data(file = "raw/IRAP 2012 VB6 format files/chad gender t1.csv",
                                  timepoint = 1)

chad_gender_IRAP2 <- wrangle_data(file = "raw/IRAP 2012 VB6 format files/chad gender t2.csv", 
                                  timepoint = 2)

chad_lincolnHitlerFriendEnemy_IRAP1 <- wrangle_data(file = "raw/IRAP 2012 VB6 format files/chad lincolnHitler FriendEnemy 1.csv", 
                                                    timepoint = 1)

chad_lincolnHitlerFriendEnemy_IRAP2 <- wrangle_data(file = "raw/IRAP 2012 VB6 format files/chad lincolnHitler FriendEnemy 2.csv", 
                                                    timepoint = 2)

chad_lincolnHitlerFriendEnemy_IRAP3 <- wrangle_data(file = "raw/IRAP 2012 VB6 format files/chad lincolnHitler FriendEnemy 3.csv", 
                                                    timepoint = 3)

chad_race_IRAP1 <- wrangle_data(file = "raw/IRAP 2012 VB6 format files/chad race t1.csv", 
                                timepoint = 1)

chad_race_IRAP2 <- wrangle_data(file = "raw/IRAP 2012 VB6 format files/chad race t2.csv", 
                                timepoint = 2)

chad_religion_IRAP1 <- wrangle_data(file = "raw/IRAP 2012 VB6 format files/chad religion t1.csv", 
                                    timepoint = 1)

chad_religion_IRAP2 <- wrangle_data(file = "raw/IRAP 2012 VB6 format files/chad religion t2.csv", 
                                    timepoint = 2)

ian_death <- wrangle_data(file = "raw/IRAP 2012 VB6 format files/ian death.csv")

# this IRAP wasn't evaluative but I include it here as it uses the function developed for them
ian_death_selfother <- wrangle_data(file = "raw/IRAP 2012 VB6 format files/ian death self other IRAP.csv") |>
  mutate(experiment = "Death (self-other)")

ian_race <- wrangle_data(file = "raw/IRAP 2012 VB6 format files/ian race 2.csv")

```

```{r}

# some exclusions needed based on a version of the task that contained an error - one block not delivered. exclude these participants.
ian_death_participants_to_retain <- ian_death |>
  filter(block_number == 1 & 
           block_type == "inconsistent") |>
  pivot_wider(names_from = trial_type,
              values_from = c(rt, accuracy)) |>
  mutate(exclude = ifelse(is.na(rt_tt1) & 
                            is.na(rt_tt2) & 
                            is.na(rt_tt3) & 
                            is.na(rt_tt4) & 
                            is.na(accuracy_tt1) & 
                            is.na(accuracy_tt2) & 
                            is.na(accuracy_tt3) & 
                            is.na(accuracy_tt4),
                          TRUE,
                          FALSE)) |>
  distinct(experiment, participant, exclude) |>
  filter(exclude == FALSE)

ian_death <- ian_death |>
  semi_join(ian_death_participants_to_retain, by = "participant")


ian_death_participants_to_retain_2 <- ian_death_selfother |>
  filter(block_number == 1 & 
           block_type == "inconsistent") |>
  pivot_wider(names_from = trial_type,
              values_from = c(rt, accuracy)) |>
  mutate(exclude = ifelse(is.na(rt_tt1) & 
                            is.na(rt_tt2) & 
                            is.na(rt_tt3) & 
                            is.na(rt_tt4) & 
                            is.na(accuracy_tt1) & 
                            is.na(accuracy_tt2) & 
                            is.na(accuracy_tt3) & 
                            is.na(accuracy_tt4),
                          TRUE,
                          FALSE)) |>
  distinct(experiment, participant, exclude) |>
  filter(exclude == FALSE)

ian_death_selfother <- ian_death_selfother |>
  semi_join(ian_death_participants_to_retain_2, by = "participant")


stigma_domains <- read_csv("raw/IRAP 2012 VB6 format files/chad mental illness stigma.csv") %>%
  filter(data_type == "Target 3 Raw Latency") %>%
  mutate(participant = as.character(participant),
         experiment = case_when(stimuli_attribute_2 == "damaged" ~ "PTSD",
                                stimuli_attribute_2 == "defective" ~ "ADHD",
                                stimuli_attribute_2 == "dangerous" ~ "schizophrenia")) |>
  select(participant, experiment)

chad_mental_illness_stigma <- chad_mental_illness_stigma |>
  select(-experiment) |>
  left_join(stigma_domains, by = "participant")
  
```

```{r}

# some domains need demographics joined in
data_demographics_temp_3 <- read_csv("raw/additional demographics data/gender rich clinton.csv") %>%
  select(participant = ParticipantNumberQualtrics, age = Age, gender = Sex) |>
  mutate(participant = as.character(participant))

chad_political_attitudes <- 
  left_join(chad_political_attitudes, data_demographics_temp_3, by = "participant")

chad_gender_IRAP1 <- 
  left_join(chad_gender_IRAP1, data_demographics_temp_3, by = "participant")

chad_gender_IRAP2 <- 
  left_join(chad_gender_IRAP2, data_demographics_temp_3, by = "participant")


data_demographics_temp_4 <- read_csv("raw/additional demographics data/stigma.csv") %>%
  select(participant = ParticipantNumber, age = Age, gender = Sex) |>
  mutate(participant = as.character(round(participant, 0)))

chad_mental_illness_stigma <- 
  left_join(chad_mental_illness_stigma, data_demographics_temp_4, by = "participant")

```

```{r}

# the lincoln hitler and friend enemy domain needs some bespoke processing
experiment_1 <- read.csv("raw/IRAP 2012 VB6 format files/chad lincolnHitler FriendEnemy 1.csv") |>
  distinct(participant, rule_1) |>
  filter(rule_1 != "") |>
  mutate(experiment = ifelse(str_detect(rule_1, "LINCOLN"), "chad lincolnhitler", "chad friendenemy")) |>
  select(-rule_1)

experiment_2 <- read.csv("raw/IRAP 2012 VB6 format files/chad lincolnHitler FriendEnemy 2.csv") |>
  distinct(participant, rule_1) |>
  filter(rule_1 != "") |>
  mutate(experiment = ifelse(str_detect(rule_1, "LINCOLN"), "chad lincolnhitler", "chad friendenemy")) |>
  select(-rule_1)

experiment_3 <- read.csv("raw/IRAP 2012 VB6 format files/chad lincolnHitler FriendEnemy 3.csv") |>
  distinct(participant, rule_1) |>
  filter(rule_1 != "") |>
  mutate(experiment = ifelse(str_detect(rule_1, "LINCOLN"), "chad lincolnhitler", "chad friendenemy")) |>
  select(-rule_1)

chad_lincolnHitlerFriendEnemy_IRAP1 <- chad_lincolnHitlerFriendEnemy_IRAP1 |>
  select(-experiment) |>
  mutate(participant = as.character(participant)) |>
  left_join(mutate(experiment_1, participant = as.character(participant)), by = "participant")

chad_lincolnHitlerFriendEnemy_IRAP2 <- chad_lincolnHitlerFriendEnemy_IRAP2 |>
  select(-experiment) |>
  mutate(participant = as.character(participant)) |>
  left_join(mutate(experiment_2, participant = as.character(participant)), by = "participant")

chad_lincolnHitlerFriendEnemy_IRAP3 <- chad_lincolnHitlerFriendEnemy_IRAP3 |>
  select(-experiment) |>
  mutate(participant = as.character(participant)) |>
  left_join(mutate(experiment_3, participant = as.character(participant)), by = "participant")


data_lincolnhitler_friendenemy_combinations <- 
  distinct(select(chad_lincolnHitlerFriendEnemy_IRAP1, participant, experiment), participant, .keep_all = TRUE) |>
  full_join(
    distinct(select(chad_lincolnHitlerFriendEnemy_IRAP2, participant, experiment), participant, .keep_all = TRUE),
    by = "participant"
  ) %>%
  full_join(
    distinct(select(chad_lincolnHitlerFriendEnemy_IRAP3, participant, experiment), participant, .keep_all = TRUE),
    by = "participant"
  ) %>%
  mutate(task_1 = dplyr::recode(experiment.x,
                                "chad lincolnhitler_1" = "HITLER",
                                "chad friendenemy_1" = "friend"),
         task_2 = dplyr::recode(experiment.y,
                                "chad lincolnhitler_2" = "HITLER",
                                "chad friendenemy_2" = "friend"),
         task_3 = dplyr::recode(experiment,
                                "chad lincolnhitler_3" = "HITLER",
                                "chad friendenemy_3" = "friend")) %>%
  select(participant, task_1, task_2, task_3) %>%
  mutate(combination = case_when(
    task_1 == task_2 & task_1 == task_3 ~ "all three", 
    task_1 == task_2 ~ "one and two", 
    task_1 == task_3 ~ "one and three", 
    task_2 == task_3 ~ "two and three"
  ))

# # chad provided a list of participants who received faking instructions, check that none were included here. the non overlap observed here demonstrates these were already excluded in manual data processing., 
# faking_instructions <- read_csv("raw/IRAP 2012 VB6 format files/chad friendenemy participants who received faking instructions.csv") %>%
#   mutate(faking_instructions = TRUE,
#          participant = as.character(participant_id)) %>%
#   select(-participant_id) %>%
#   full_join(data_lincolnhitler_friendenemy_combinations, by = "participant")

# logic for assigning IRAPs within-domain timepoints, for test-retest reliability  
chad_lincolnHitlerFriendEnemy_IRAP1 <- chad_lincolnHitlerFriendEnemy_IRAP1 %>%
  mutate(timepoint = 1)

chad_lincolnHitlerFriendEnemy_IRAP2 <- chad_lincolnHitlerFriendEnemy_IRAP2 %>%
  mutate(timepoint = ifelse(participant %in% 
                              pull(filter(data_lincolnhitler_friendenemy_combinations, 
                                          combination %in% c("all three", "one and two")), participant),
                            2, 1))

chad_lincolnHitlerFriendEnemy_IRAP3 <- chad_lincolnHitlerFriendEnemy_IRAP3 %>%
  mutate(timepoint = ifelse(participant %in% 
                              pull(filter(data_lincolnhitler_friendenemy_combinations, 
                                          combination %in% c("one and three", "two and three")), participant),
                            2, 
                            ifelse(participant %in% 
                                     pull(filter(data_lincolnhitler_friendenemy_combinations, 
                                                 combination %in% c("all three")), participant),
                                   NA, 1)))

data_demographics_temp_2 <- read_csv("raw/additional demographics data/lincoln friend.csv") %>%
  select(participant, age, gender = sex) |>
  mutate(participant = as.character(participant))

chad_lincolnHitlerFriendEnemy_IRAP1 <- 
  left_join(chad_lincolnHitlerFriendEnemy_IRAP1, data_demographics_temp_2, by = "participant")

chad_lincolnHitlerFriendEnemy_IRAP2 <- 
  left_join(chad_lincolnHitlerFriendEnemy_IRAP2, data_demographics_temp_2, by = "participant")

chad_lincolnHitlerFriendEnemy_IRAP3 <- 
  left_join(chad_lincolnHitlerFriendEnemy_IRAP3, data_demographics_temp_2, by = "participant")

```

```{r}

# combine
combined_data <- 
  bind_rows(chad_political_attitudes,
            chad_mental_illness_stigma,
            chad_bodyImage_IRAP1,
            chad_bodyImage_IRAP2,
            chad_gender_IRAP1,
            chad_gender_IRAP2,
            chad_lincolnHitlerFriendEnemy_IRAP1,
            chad_lincolnHitlerFriendEnemy_IRAP2,
            chad_lincolnHitlerFriendEnemy_IRAP3,
            chad_race_IRAP1,
            chad_race_IRAP2,
            chad_religion_IRAP1,
            chad_religion_IRAP2,
            ian_death,
            ian_death_selfother,
            ian_race) |>
  mutate(experiment = str_remove(experiment, "IRAP"),
         experiment = str_remove(experiment, "_1"),
         experiment = str_remove(experiment, "_2"),
         experiment = str_remove(experiment, "_3"),
         experiment = str_remove(experiment, "_")) |>
  mutate(unique_id = paste(experiment, participant, sep = "_")) 

## get demographics data
data_demographics_temp_1 <- read_csv("raw/IRAP 2012 VB6 format files/demographics and performance criteria data.csv") %>%
  select(unique_id, age, gender)

data_evaluative_temp <- 
  left_join(combined_data, data_demographics_temp_1, by = "unique_id")

# filter out participants who do not have the correct number of trials
data_evaluative <- data_evaluative_temp |>
  semi_join(data_evaluative_temp |>
              count(unique_id, timepoint) |>
              filter(n %in% c(144, 192)),
            by = c("unique_id", "timepoint")) |>
  mutate(age = case_when(!is.na(age.x) ~ age.x,
                         !is.na(age.y) ~ age.y),
         gender = case_when(!is.na(gender.x) ~ gender.x,
                            !is.na(gender.y) ~ gender.y)) |>
  select(unique_id, experiment, participant, age, gender, timepoint, block_order, 
         stimulus_number, block_number, block_type, trial_type, rt, accuracy)

# data_evaluative |>
#   distinct(unique_id, .keep_all = TRUE) |>
#   count(experiment, missing = is.na(age))

```

## Nonevaluative IRAPs

### Multiple domains

```{r}

## process data that was output by/formatted from the VB6 2012+ IRAP
data_input <- bind_rows(read_csv("raw/IRAP 2012 VB6 format files/ian countries 1.csv"),
                        read_csv("raw/IRAP 2012 VB6 format files/ian disgust 2.csv"),
                        read_csv("raw/IRAP 2012 VB6 format files/ian sexuality 2.csv"),
                        read_csv("raw/IRAP 2012 VB6 format files/ian valenced words.csv"),
                        read_csv("raw/IRAP 2012 VB6 format files/ian shapes and colors study 2.csv"),
                        read_csv("raw/IRAP 2012 VB6 format files/ian shapes and colors study 3.csv")) %>%
  mutate(stimulus_number = str_remove_all(trial_and_data_type, " Raw Latency")) %>%
  select(unique_id, participant, experiment, block_order, stimulus_number, trial_and_data_type, 
         tt1_block1_con, tt2_block1_con, tt3_block1_con, tt4_block1_con, 
         tt1_block1_incon, tt2_block1_incon, tt3_block1_incon, tt4_block1_incon, 
         tt1_block2_con, tt2_block2_con, tt3_block2_con, tt4_block2_con, 
         tt1_block2_incon, tt2_block2_incon, tt3_block2_incon, tt4_block2_incon, 
         tt1_block3_con, tt2_block3_con, tt3_block3_con, tt4_block3_con, 
         tt1_block3_incon, tt2_block3_incon, tt3_block3_incon, tt4_block3_incon)

data_completeness <- data_input %>%
  gather(trial_and_block, rt, c("tt1_block1_con", "tt2_block1_con", "tt3_block1_con", "tt4_block1_con", 
                                "tt1_block1_incon", "tt2_block1_incon", "tt3_block1_incon", "tt4_block1_incon", 
                                "tt1_block2_con", "tt2_block2_con", "tt3_block2_con", "tt4_block2_con", 
                                "tt1_block2_incon", "tt2_block2_incon", "tt3_block2_incon", "tt4_block2_incon", 
                                "tt1_block3_con", "tt2_block3_con", "tt3_block3_con", "tt4_block3_con", 
                                "tt1_block3_incon", "tt2_block3_incon", "tt3_block3_incon", "tt4_block3_incon")) %>%
  count(unique_id) %>%
  filter(n %in% c(288, 480)) # methodologically plausible number of trials

data_nonevaluative_rt <- data_input %>%
  semi_join(data_completeness, by = "unique_id") %>%
  filter(str_detect(trial_and_data_type, "Raw Latency")) %>%
  gather(trial_and_block, rt, c("tt1_block1_con", "tt2_block1_con", "tt3_block1_con", "tt4_block1_con", 
                                "tt1_block1_incon", "tt2_block1_incon", "tt3_block1_incon", "tt4_block1_incon", 
                                "tt1_block2_con", "tt2_block2_con", "tt3_block2_con", "tt4_block2_con", 
                                "tt1_block2_incon", "tt2_block2_incon", "tt3_block2_incon", "tt4_block2_incon", 
                                "tt1_block3_con", "tt2_block3_con", "tt3_block3_con", "tt4_block3_con", 
                                "tt1_block3_incon", "tt2_block3_incon", "tt3_block3_incon", "tt4_block3_incon")) %>%
  separate(trial_and_block, into = c("trial_type", "block", "block_type"), sep = "_") %>%
  select(unique_id, block_type, trial_type, stimulus_number, rt, experiment, participant, block_order)

data_nonevaluative_acc <- data_input %>%
  semi_join(data_completeness, by = "unique_id") %>%
  filter(str_detect(trial_and_data_type, "Accuracy")) %>%
  mutate(stimulus_number = str_remove_all(trial_and_data_type, " Accuracy")) %>%
  gather(trial_and_block, accuracy, c("tt1_block1_con", "tt2_block1_con", "tt3_block1_con", "tt4_block1_con", 
                                      "tt1_block1_incon", "tt2_block1_incon", "tt3_block1_incon", "tt4_block1_incon", 
                                      "tt1_block2_con", "tt2_block2_con", "tt3_block2_con", "tt4_block2_con", 
                                      "tt1_block2_incon", "tt2_block2_incon", "tt3_block2_incon", "tt4_block2_incon", 
                                      "tt1_block3_con", "tt2_block3_con", "tt3_block3_con", "tt4_block3_con", 
                                      "tt1_block3_incon", "tt2_block3_incon", "tt3_block3_incon", "tt4_block3_incon")) %>%
  separate(trial_and_block, into = c("trial_type", "block", "block_type"), sep = "_") %>%
  select(unique_id, block_type, trial_type, stimulus_number, experiment, participant, block_order, accuracy)

data_nonevaluative <- data_nonevaluative_rt |>
  bind_cols(data_nonevaluative_acc |> select(accuracy)) |>
  mutate(timepoint = 1) |>
  mutate(stimulus_number = tolower(str_remove(stimulus_number, " ")),
         block_order = str_remove(block_order, " first"),
         block_order = dplyr::recode(tolower(block_order),
                                     "con" = "consistent first",
                                     "incon" = "inconsistent first"),
         block_type = dplyr::recode(tolower(block_type),
                                    "con" = "consistent",
                                    "incon" = "inconsistent")) |>
  select(unique_id, experiment, participant, 
         #age, gender, 
         timepoint, block_order, 
         stimulus_number, 
         #block_number, 
         block_type, trial_type, rt, accuracy)

```

### Disgust 1

```{r}

data_input_disgust <- read_csv("raw/IRAP 2012 VB6 format files/ian disgust 1.csv") 

data_completeness <- data_input_disgust %>%
  gather(trial_and_block, rt, c("tt1_block1_con", "tt2_block1_con", "tt3_block1_con", "tt4_block1_con", 
                                "tt1_block1_incon", "tt2_block1_incon", "tt3_block1_incon", "tt4_block1_incon", 
                                "tt1_block2_con", "tt2_block2_con", "tt3_block2_con", "tt4_block2_con", 
                                "tt1_block2_incon", "tt2_block2_incon", "tt3_block2_incon", "tt4_block2_incon", 
                                "tt1_block3_con", "tt2_block3_con", "tt3_block3_con", "tt4_block3_con", 
                                "tt1_block3_incon", "tt2_block3_incon", "tt3_block3_incon", "tt4_block3_incon",
                                "tt1_block4_con", "tt2_block4_con", "tt3_block4_con", "tt4_block4_con", 
                                "tt1_block4_incon", "tt2_block4_incon", "tt3_block4_incon", "tt4_block4_incon", 
                                "tt1_block5_con", "tt2_block5_con", "tt3_block5_con", "tt4_block5_con", 
                                "tt1_block5_incon", "tt2_block5_incon", "tt3_block5_incon", "tt4_block5_incon", 
                                "tt1_block6_con", "tt2_block6_con", "tt3_block6_con", "tt4_block6_con", 
                                "tt1_block6_incon", "tt2_block6_incon", "tt3_block6_incon", "tt4_block6_incon")) %>%
  count(unique_id) %>%
  filter(n %in% c(384*2)) # methodologically plausible number of trials

data_disgust_1 <- data_input_disgust %>%
  semi_join(data_completeness, by = c("unique_id")) %>%
  #filter(str_detect(trial_and_data_type, "Raw Latency")) %>%
  gather(trial_and_block, response, c("tt1_block1_con", "tt2_block1_con", "tt3_block1_con", "tt4_block1_con", 
                                      "tt1_block1_incon", "tt2_block1_incon", "tt3_block1_incon", "tt4_block1_incon", 
                                      "tt1_block2_con", "tt2_block2_con", "tt3_block2_con", "tt4_block2_con", 
                                      "tt1_block2_incon", "tt2_block2_incon", "tt3_block2_incon", "tt4_block2_incon", 
                                      "tt1_block3_con", "tt2_block3_con", "tt3_block3_con", "tt4_block3_con", 
                                      "tt1_block3_incon", "tt2_block3_incon", "tt3_block3_incon", "tt4_block3_incon",
                                      "tt1_block4_con", "tt2_block4_con", "tt3_block4_con", "tt4_block4_con", 
                                      "tt1_block4_incon", "tt2_block4_incon", "tt3_block4_incon", "tt4_block4_incon", 
                                      "tt1_block5_con", "tt2_block5_con", "tt3_block5_con", "tt4_block5_con", 
                                      "tt1_block5_incon", "tt2_block5_incon", "tt3_block5_incon", "tt4_block5_incon", 
                                      "tt1_block6_con", "tt2_block6_con", "tt3_block6_con", "tt4_block6_con", 
                                      "tt1_block6_incon", "tt2_block6_incon", "tt3_block6_incon", "tt4_block6_incon")) %>%
  separate(trial_and_block, into = c("trial_type", "block", "block_type"), sep = "_") %>%
  mutate(timepoint = ifelse(str_detect(block, "block1") | 
                              str_detect(block, "block2") | 
                              str_detect(block, "block3"), 1, 2),
         experiment = "Disgust (1)") |>
  # wrangle acc vs rt
  mutate(trial_and_data_type = str_replace(trial_and_data_type, "Target ", "target"),
         trial_and_data_type = str_replace(trial_and_data_type, "Raw Latency", "rt"),
         trial_and_data_type = str_remove(trial_and_data_type, ":"),
         trial_and_data_type = str_replace(trial_and_data_type, "Accuracy", "accuracy")) |>
  separate(trial_and_data_type, into = c("stimulus_number", "data_type"), sep = " ") |>
  pivot_wider(names_from = data_type, 
              values_from = "response") |>
  mutate(block_order = dplyr::recode(block_order,
                                     "con first" = "consistent first",
                                     "incon first" = "inconsistent first"),
         block_type = dplyr::recode(block_type,
                                    "con" = "consistent",
                                    "incon" = "inconsistent"),
         block_number = as.numeric(str_remove(block, "block"))) |>
  select(unique_id, experiment, participant, 
         #age, gender, 
         timepoint, block_order, 
         stimulus_number, 
         block_number, 
         block_type, trial_type, rt, accuracy)

# join demographics
data_demographics_temp_digust <- 
  read_csv("raw/additional demographics data/disgust 1 explicits and bats.csv") %>%
  select(participant, age, gender) |>
  mutate(participant = paste0(as.character(participant), "I"))

data_disgust_1 <- 
  left_join(data_disgust_1, data_demographics_temp_digust, by = "participant")

```

### Sexuality 1

```{r}

data_input_sexuality <- read_csv("raw/IRAP 2012 VB6 format files/ian sexuality 1.csv")

data_completeness <- data_input_sexuality %>%
  gather(trial_and_block, rt, c("tt1_block1_con", "tt2_block1_con", "tt3_block1_con", "tt4_block1_con", 
                                "tt1_block1_incon", "tt2_block1_incon", "tt3_block1_incon", "tt4_block1_incon", 
                                "tt1_block2_con", "tt2_block2_con", "tt3_block2_con", "tt4_block2_con", 
                                "tt1_block2_incon", "tt2_block2_incon", "tt3_block2_incon", "tt4_block2_incon", 
                                "tt1_block3_con", "tt2_block3_con", "tt3_block3_con", "tt4_block3_con", 
                                "tt1_block3_incon", "tt2_block3_incon", "tt3_block3_incon", "tt4_block3_incon")) %>%
  count(unique_id, timepoint) %>%
  filter(n %in% c(480)) # methodologically plausible number of trials

data_sexuality_1 <- data_input_sexuality %>%
  semi_join(data_completeness, by = c("unique_id", "timepoint")) %>%
  #filter(str_detect(trial_and_data_type, "Raw Latency")) %>%
  pivot_longer(cols = starts_with("tt"),
               names_to = "trial_and_block", 
               values_to = "response") %>%
  mutate(trial_and_data_type = str_replace(trial_and_data_type, "Target ", "target"),
         trial_and_data_type = str_replace(trial_and_data_type, "Raw Latency", "rt"),
         trial_and_data_type = str_remove(trial_and_data_type, ":"),
         trial_and_data_type = str_replace(trial_and_data_type, "Accuracy", "accuracy")) |>
  separate(trial_and_data_type, into = c("stimulus_number", "data_type"), sep = " ") |>
  pivot_wider(names_from = data_type, 
              values_from = "response") |>
  separate(trial_and_block, into = c("trial_type", "block", "block_type"), sep = "_") %>%
  # drop practice blocks
  filter(!str_detect(block, "prac")) |>
  mutate(experiment = "Sexuality (1)") %>%
  # wrangle acc vs rt
  mutate(block_order = dplyr::recode(block_order,
                                     "con first" = "consistent first",
                                     "incon first" = "inconsistent first"),
         block_type = dplyr::recode(block_type,
                                    "con" = "consistent",
                                    "incon" = "inconsistent"),
         participant = as.factor(participant),
         block_number = as.numeric(str_remove(block, "block"))) |>
  select(unique_id, experiment, participant, 
         #age, gender, 
         timepoint, block_order, 
         stimulus_number, 
         block_number, 
         block_type, trial_type, rt, accuracy)

```

### Personality IRAPs

```{r}

## process data from 2012 IRAP from Chad wave 2
chad_personality_temp <- read_csv("raw/IRAP 2012 VB6 format files/chad personality.csv") %>%
  mutate(participant = as.factor(participant)) %>%
  select(-contains("fp_"), -block_order) %>%
  mutate_at(vars(-experiment, -participant, -data_type, 
                 -stimuli_category_1, -stimuli_category_2, -stimuli_attribute_1, -stimuli_attribute_2), as.character) %>%
  mutate_at(vars(-experiment, -participant, -data_type, 
                 -stimuli_category_1, -stimuli_category_2, -stimuli_attribute_1, -stimuli_attribute_2), as.numeric) %>%
  mutate_at(vars(experiment, participant, data_type, 
                 stimuli_category_1, stimuli_category_2, stimuli_attribute_1, stimuli_attribute_2), as.character) %>%
  #filter(grepl("Target", data_type) & grepl("Latency", data_type)) %>%
  right_join(read_csv("raw/IRAP 2012 VB6 format files/chad personality.csv") %>%
               mutate(participant = as.factor(participant)) %>%
               select(participant, block_order) %>%
               distinct(participant, .keep_all = TRUE), by = "participant") %>%
  mutate(block_order = dplyr::recode(block_order,
                                     "The Consistent-First Sequence was Selected" = "Consistent",
                                     "The Inconsistent-First Sequence was Selected" = "Inconsistent",
                                     "Consistant" = "Consistent",
                                     "Inconsistant" = "Inconsistent")) 

# full names were used as participants codes to link data - anonymize
chad_personality_ids <- chad_personality_temp %>%
  distinct(participant) %>%
  rownames_to_column(var = "anonymized_participant")

chad_personality_temp_2 <- chad_personality_temp %>%
  full_join(chad_personality_ids, by = "participant") %>%
  semi_join(chad_personality_temp |>
              count(participant) |>
              filter(n == 60),
            by = "participant") |>
  select(-participant, -stimuli_category_1, -stimuli_category_2, -stimuli_attribute_1, -stimuli_attribute_2) %>%
  rename(participant = anonymized_participant) %>%
  mutate(timepoint = 1,
         unique_id = paste(experiment, participant, sep = "_")) %>%
  pivot_longer(cols = starts_with("t1_") | starts_with("t2_") | starts_with("t3_"),
               names_to = "type",
               values_to = "response") %>%
  separate(type, into = c("blockpair_number", "block_type", "trial_type")) %>%
  # wrangle acc vs rt
  mutate(data_type = str_replace(data_type, "Target ", "target"),
         data_type = str_replace(data_type, "Raw Latency", "rt"),
         data_type =  str_remove(data_type, ":"),
         data_type = str_replace(data_type, "Accuracy", "accuracy")) |>
  separate(data_type, into = c("stimulus_number", "data_type"), sep = " ") |>
  pivot_wider(names_from = "data_type", 
              values_from = "response") |>
  # wrangle acc vs rt
  mutate(block_order = dplyr::recode(block_order,
                                     "Consistent" = "consistent first",
                                     "Inconsistent" = "inconsistent first"),
         block_type = dplyr::recode(block_type,
                                    "c" = "consistent",
                                    "ic" = "inconsistent"),
         block_number = as.numeric(str_remove(blockpair_number, "t"))) |>
  select(unique_id, experiment, participant, 
         #age, gender, 
         timepoint, block_order, 
         stimulus_number, 
         block_number, 
         block_type, trial_type, rt, accuracy)

## get demographics data
data_demographics_personality <- 
  read_csv("raw/additional demographics data/personality.csv") %>%
  select(participant = Participant, age = Age, gender = Sex) |>
  mutate(participant = as.character(participant))

chad_personality <- 
  left_join(chad_personality_temp_2, data_demographics_personality, by = "participant")

```

# GO-IRAP format files

```{r}

data_goirap <- 
  bind_rows(
    read_csv("raw/GO-IRAP format files/aoife negative gender stereotypes IRAP dataset raw.csv", show_col_types = FALSE) %>%
      select(participant,
             experiment,
             gender,
             age,
             block_order = startingRule,
             block_number = blockPairNumber,
             stimulus_number = targetNum,
             block_type = currentRule,
             trial_type = trialType,
             rt,
             accuracy,
             isTestBlock) |>
      mutate(participant = as.character(participant),
             unique_id = paste(experiment, participant),
             stimulus_number = paste0("target", stimulus_number)),
    read_csv("raw/GO-IRAP format files/aoife positive gender stereotypes IRAP dataset raw - used in De Schryver 2017.csv", show_col_types = FALSE) %>%
      mutate(experiment = "Gender stereotypes positive") |>
      select(participant = unique_participant_identifier,
             experiment,
             gender,
             age,
             block_order = starting_rule,
             block_number = blockPairNumber,
             stimulus_number = targetNum,
             block_type = currentRule,
             trial_type = trialType,
             rt,
             accuracy,
             isTestBlock) |>
      mutate(participant = as.character(participant),
             unique_id = paste(experiment, participant),
             stimulus_number = paste0("target", stimulus_number)),
    read_csv("raw/GO-IRAP format files/ian countries 2 acknowledge.csv", show_col_types = FALSE) %>%
      select(participant = unique_id,
             experiment,
             gender = participantGender,
             age = participantAge,
             block_order = startingRule,
             block_number = blockPairNumber,
             stimulus_number = targetNum,
             block_type = currentRule,
             trial_type = trialType,
             rt = timeToCorrectResponse,
             accuracy,
             isTestBlock) |>
      mutate(stimulus_number = paste0("target", stimulus_number),
             unique_id = paste(experiment, participant)),
    read_csv("raw/GO-IRAP format files/ian countries 2 care.csv", show_col_types = FALSE) %>%
      select(participant = unique_id,
             experiment,
             gender = participantGender,
             age = participantAge,
             block_order = startingRule,
             block_number = blockPairNumber, # TODO
             stimulus_number = targetNum, # TODO
             block_type = currentRule,
             trial_type = trialType,
             rt = timeToCorrectResponse,
             accuracy,
             isTestBlock) |>
      mutate(stimulus_number = paste0("target", stimulus_number),
             unique_id = paste(experiment, participant)),
    read_csv("raw/GO-IRAP format files/ian shapes and colors 1 YNrule.csv", show_col_types = FALSE) %>%
      select(unique_id, 
             experiment, 
             participant = participantCode, 
             age = participantAge, 
             gender = participantGender,
             # timepoint, 
             block_order = startingRule, 
             stimulus_number = target, 
             block_number = blockPairNumber,
             block_type = currentRule, 
             trial_type = trialType, 
             rt = timeToCorrectResponse, 
             accuracy,
             isTestBlock) |>
      mutate(participant = as.character(participant),
             stimulus_number = dplyr::recode(stimulus_number, 
                                             "Square" = "target1",		
                                             "Triangle" = "target2",
                                             "Circle" = "target3",				
                                             "Blue" = "target1",		
                                             "Red" = "target2",			
                                             "Green" = "target3")),
    read_csv("raw/GO-IRAP format files/ian shapes and colors 2 YNcorrect.csv", show_col_types = FALSE) %>%
      select(unique_id, 
             experiment, 
             participant = participantCode, 
             age = participantAge, 
             gender = participantGender,
             # timepoint, 
             block_order = startingRule, 
             stimulus_number = target, 
             block_number = blockPairNumber,
             block_type = currentRule, 
             trial_type = trialType, 
             rt = timeToCorrectResponse, 
             accuracy,
             isTestBlock) |>
      mutate(participant = as.character(participant),
             stimulus_number = dplyr::recode(stimulus_number, 
                                             "Square" = "target1",		
                                             "Triangle" = "target2",
                                             "Circle" = "target3",				
                                             "Blue" = "target1",		
                                             "Red" = "target2",			
                                             "Green" = "target3")),
    read_csv("raw/GO-IRAP format files/ian shapes and colors 3 TFcorrect.csv", show_col_types = FALSE) %>%
      select(unique_id, 
             experiment, 
             participant = participantCode, 
             age = participantAge, 
             gender = participantGender,
             # timepoint, 
             block_order = startingRule, 
             stimulus_number = target, 
             block_number = blockPairNumber,
             block_type = currentRule, 
             trial_type = trialType, 
             rt = timeToCorrectResponse, 
             accuracy,
             isTestBlock) |>
      mutate(participant = as.character(participant),
             stimulus_number = dplyr::recode(stimulus_number, 
                                             "Square" = "target1",		
                                             "Triangle" = "target2",
                                             "Circle" = "target3",				
                                             "Blue" = "target1",		
                                             "Red" = "target2",			
                                             "Green" = "target3")),
    read_csv("raw/GO-IRAP format files/ian shapes and colors 4 TFrule.csv", show_col_types = FALSE) %>%
      select(unique_id, 
             experiment, 
             participant = participantCode, 
             age = participantAge, 
             gender = participantGender,
             # timepoint, 
             block_order = startingRule, 
             stimulus_number = target, 
             block_number = blockPairNumber,
             block_type = currentRule, 
             trial_type = trialType, 
             rt = timeToCorrectResponse, 
             accuracy,
             isTestBlock) |>
      mutate(participant = as.character(participant),
             stimulus_number = dplyr::recode(stimulus_number, 
                                             "Square" = "target1",		
                                             "Triangle" = "target2",
                                             "Circle" = "target3",				
                                             "Blue" = "target1",		
                                             "Red" = "target2",			
                                             "Green" = "target3"))
  ) %>%
  filter(isTestBlock == 1) %>%
  mutate(block_type = dplyr::recode(block_type,
                                    `1` = "consistent",
                                    `2` = "inconsistent"),
         block_order = dplyr::recode(block_order,
                                     `1` = "consistent first",
                                     `2` = "inconsistent first"),
         trial_type = dplyr::recode(trial_type,
                                    `1` = "tt1",
                                    `2` = "tt2",
                                    `3` = "tt3",
                                    `4` = "tt4"),
         timepoint = 1) |>
  # wrangle acc vs rt
  select(unique_id, 
         experiment, 
         participant, 
         age, 
         gender, 
         timepoint, 
         block_order, 
         stimulus_number, 
         block_number, 
         block_type, 
         trial_type, 
         rt, 
         accuracy)

```

# Nonwords

```{r}

data_nonwords <- read_csv("raw/non-words/data_trial_level_nonwords.csv") |>
  mutate(unique_id = paste(experiment, participant),
         participant = as.character(participant))

```

# Combine

```{r}

data_trial_level_temp_1 <- 
  bind_rows(data_evaluative,
            data_nonevaluative,
            data_disgust_1,
            data_sexuality_1,
            chad_personality,
            data_goirap,
            data_nonwords) %>%
  rename(domain = experiment) %>%
  mutate(domain = dplyr::recode(domain,
                                "clintontrump" = "Clinton-Trump",				
                                "richpoor" = "Rich-Poor",
                                "ADHD" = "Stigma - ADHD",				
                                "PTSD" = "Stigma - PTSD",				
                                "schizophrenia" = "Stigma - Schizophrenia",
                                "agreeableness" = "Personality - Agreeableness",
                                "conscientiousness" = "Personality - Conscientiousness",
                                "extraversion" = "Personality - Extraversion",
                                "neuroticism" = "Personality - Neuroticism",
                                "openness" = "Personality - Openness",
                                "chad bodyimage" = "Body image",
                                "chad friendenemy" = "Friend-Enemy",
                                "chad gender" = "Gender stereotypes (1)", # chad's dataset
                                "menwomen" = "Gender stereotypes (2)",	# ian's dataset
                                "Gender stereotypes positive" = "Gender stereotypes (3)", # aoife's datasets
                                "Gender stereotypes negative" = "Gender stereotypes (4)", # aoife's datasets
                                "chad lincolnhitler" = "Lincoln-Hitler",
                                "chad race"	 = "Race (1)",
                                "ian race" = "Race (2)",
                                "chad religion" = "Religion",
                                "ian death emma" = "Death (1)",
                                "ian death june" = "Death (2)",
                                "ian death tarah" = "Death (3)",
                                "Death (self-other)" = "Death (4)",
                                "Disgust (1)" = "Disgust (1)",
                                "Disgust (2)" = "Disgust (2)",
                                "Sexuality (1)" = "Sexuality (1)",
                                "Sexuality (2)" = "Sexuality (2)",
                                "countries acknowledge 1" = "Countries (1)",
                                "countries care 1" = "Countries (2)",
                                "countries 2 acknowledge" = "Countries (3)",
                                "countries 2 care" = "Countries (4)",
                                "valenced words" = "Valenced words",
                                "shapes and colors 1 yesno fullrule" = "Shapes & colors (1)",
                                "shapes and colors 2 yesno respondcorrectly" = "Shapes & colors (2)",
                                "shapes and colors 3 truefalse respondcorrectly" = "Shapes & colors (3)",
                                "shapes and colors 4 truefalse fullrule" = "Shapes & colors (4)",
                                "shapes and colors exp 2 full rule" = "Shapes & colors (5)",
                                "shapes and colors exp 2 minimal rule" = "Shapes & colors (6)",
                                "shapes and colors exp 3" = "Shapes & colors (7)",
                                "Non-words" = "Non-words")) %>%
  arrange(as.character(domain))


# performance stats
performance_criteria_typical <- data_trial_level_temp_1 |>
  group_by(unique_id, timepoint, block_type) %>%
  summarize(median_rt = janitor::round_half_up(median(rt, na.rm = TRUE), 0),
            percent_accuracy = janitor::round_half_up(mean(accuracy, na.rm = TRUE), 2)) %>%
  ungroup() |>
  pivot_wider(names_from = "block_type",
              values_from = c("median_rt", "percent_accuracy")) |>
  mutate(met_performance_criteria_typical = 
           ifelse(median_rt_consistent <= 2000 & 
                    median_rt_inconsistent <= 2000 & 
                    percent_accuracy_consistent >= .78 &
                    percent_accuracy_inconsistent >= .78, TRUE, FALSE)) |>
  select(unique_id, timepoint, met_performance_criteria_typical)

performance_criteria_stricter <- data_trial_level_temp_1 |>
  group_by(unique_id, timepoint, block_type, block_number) |>
  summarize(median_rt = janitor::round_half_up(median(rt, na.rm = TRUE), 0),
            percent_accuracy = janitor::round_half_up(mean(accuracy, na.rm = TRUE), 2),
            .groups = "drop") |>
  pivot_wider(names_from = c("block_type", "block_number"),
              values_from = c("median_rt", "percent_accuracy")) |>
  mutate(met_performance_criteria_stricter = 
           ifelse(median_rt_consistent_1 <= 2000 & 
                    median_rt_consistent_2 <= 2000 & 
                    median_rt_consistent_3 <= 2000 & 
                    median_rt_inconsistent_1 <= 2000 & 
                    median_rt_inconsistent_2 <= 2000 & 
                    median_rt_inconsistent_3 <= 2000 & 
                    percent_accuracy_consistent_1 >= .78 &
                    percent_accuracy_consistent_2 >= .78 &
                    percent_accuracy_consistent_3 >= .78 &
                    percent_accuracy_inconsistent_1 >= .78 &
                    percent_accuracy_inconsistent_2 >= .78 &
                    percent_accuracy_inconsistent_3 >= .78, TRUE, FALSE)) |>
  select(unique_id, timepoint, met_performance_criteria_stricter)

# combine
data_trial_level_temp_2 <- data_trial_level_temp_1 |>
  left_join(performance_criteria_typical, by = c("unique_id", "timepoint")) |>
  left_join(performance_criteria_stricter, by = c("unique_id", "timepoint")) |>
  # mark odd vs even trials
  group_by(unique_id, timepoint) %>%
  mutate(row_id = row_number()) %>%
  ungroup() %>%
  mutate(trial_odd_even = ifelse(row_id %% 2 == 1, "odd", "even")) 


# join in task parameters
data_trial_level_temp_3 <- data_trial_level_temp_2 %>%
  left_join(data_task_parameters, by = "domain")

# final tidying
data_trial_level <- data_trial_level_temp_3 |>
  # remove spurious age data
  mutate(age = ifelse(age > 999, NA, age),
         age = ifelse(age < 18, NA, age)) |>
  # order columns
  select(
    # participant details
    unique_id, 
    timepoint, 
    domain, 
    participant, 
    age, 
    gender, 
    # performance criteria
    met_performance_criteria_typical, 
    met_performance_criteria_stricter, 
    # procedural details
    trials_per_block, 
    response_option_locations,
    block_order_between_participants,
    # condition and trial details
    block_order, 
    block_number, 
    block_type, 
    trial_type, 
    stimulus_number, 
    trial_odd_even,
    # responses
    rt, 
    accuracy,
    # publication status
    data_published,
    measure_published
  )

# write to disk
write_csv(data_trial_level, "data_trial_level.csv")

#data_trial_level <- read_csv("data_trial_level.csv")

```

# Session info

```{r}

sessionInfo()

```


